
\documentclass[margin,11pt]{res}

\begin{document}
\name{LI GE\\[12pt]}

\address{{\bf Address} \\  8870 Villa La Jolla Drive  \\ La Jolla, CA 92037 \\ (858) 888-2583}
\address{ {\bf Email:} geli19880206@gmail.com \\ {\bf Website:} lige.me \\ {\bf Github:} lge88}


\begin{resume}

  \section{OBJECTIVE}
  Software Engineer - Web Applications OR
  Software Engineer - Web Applications / Media \& Platform Tools

  \section{EDUCATION}
  B.S., Hydraulic Engineering, Tsinghua University, Beijing, China \\
  GPA: 89.4/100, rank: 8/90 \\
  M.S., Structural Engineering, University of California, San Diego, CA, U.S. \\
  GPA: 3.929/4

  \section{WEB APPLICATION EXPERIENCE}
  SketchIT project:
  \begin{itemize}
  \item[] Developed a sketch-based modeling and simulation application for structural analysis.
  \item[] Wrote the user interface using JavaScript, HTML, CSS.
  \item[] Implemented a template-based sketch recognize algorithm in JavaScript.
  \item[] Developed a visualization module using HTML5 canvas API.
  \item[] Implemented a Finite Element Analysis (FEA) module in C and C++.
  \item[] Wrote a Websocket server using Node.js to wrap the FEA module.
  \item[] Demo: http://www.youtube.com/watch?v=v0Z8Bou6g1A
  \item[] Website: http://vision2.ucsd.edu/
  \end{itemize}

  ARStructure project:
  \begin{itemize}
  \item[] Developed a IOS Augmented Reality (AR) application for structure simulation and visualization.
  \item[] Wrote user interface in UIWebView using JavaScript, HTML, CSS.
  \item[] Managed more than 40 web components in the project using Node.js `component' module system.
  \item[] Developed a set of custom build middlewares and component templates.
  \item[] Wrote AR Tracking interface in Object-C.
  \item[] Implemented a JavaScript bridge to communicate with native AR module.
  \item[] Used WebGL to visualize the 3D structure model.
  \end{itemize}

  \section{SKILLS}
  JavaScript, Node.js, HTML, CSS, WebGL, C/C++, Object-C, emacs, Unix/Linux

  \section{HONORS}
  Research Award, University of California, San Diego, 2010 -- 2011 \\
  Sports Star (annual award to top 10 athletes), Tsinghua University, 2009 \\
  3rd prize in 7th National Zhou Peiyuan Mechanics Competition of China, 2009 \\
  2nd prize in 24th National Undergraduate Physical Contest of China, 2007

\end{resume}
\end{document}
